Testing atlantisom: generate census length comps

### 2019-05-11 TrueLengthCompTest.Rmd
final text adjustments

To do the proper aggregation and not apply the multinomial sampling to the density data, I rewrite `sample_fish` to apply the median if `sample=FALSE` in the function call. Test this:

>>>>

To do the proper aggregation and not apply the multinomial sampling to the density data, I rewrote `sample_fish` to apply the median if `sample=FALSE` in the function call. Test this:
